---
title: "Components of the strategy"
author: "Vik Sharma"
date: "4/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Identifying trend 

## Indicator Ideas 
1. Estimate slope over a look back period 
2. Calculate rate of change of slope over last n periods 
3. Use moving averages 

*Note* Use volume weighted price to identify trend? 

## TTR indicators 
1. aroon - identifies start of trend by measuring time since lowest low/ highest high 
2. CCI - identifies start/end of trend by relating current price and average price over last n periods 
3. VHF - n-period low - n-period high / n-period sum of price changes 
4. GMMA - uses a group of short and long MA to generate trend direction 

## Application 

```{r}
library(data.table)
library(xts)
library(readr)
library(TTR)
```


```{r}
#import data 
aapl <- fread("appl-1983-1995.csv", drop=c(1,3))
aapl <- as.xts(data.frame(aapl[,c(2,3,4)]), order.by=as.Date(aapl[[1]], "%d-%m-%y"))

# find missing values 
sum(is.na(aapl[,3]))

# drop one missing observation 
dim(aapl)
aapl <- aapl[-which(is.na(aapl[,3]))]
dim(aapl)

#generate rolling 5-day volume weighted average price 
vwap <- vector()
for (i in 6:dim(aapl)[1]){
  sbset <- aapl[(i-5):i]
  vwap <- c(vwap,sum(sbset[,1]*sbset[,2])/sum(sbset[,2]))
}

aapl_vwap <- as.xts(c(rep(0,5),vwap), order.by = index(aapl)) 
head(aapl_vwap)
```


## Create Indicator functions 
```{r}
TREND <- function(prices, n){
  
  sl <- vector()
  
  for (i in (1+n):dim(prices)[1]){
  sbset <- prices[(i-n):(i-1)]
  sl <- c(sl, coef(lm(sbset[,1] ~ c(1:n)))[[2]])
  }
  
  return(as.xts(c(rep(0,n), sl), order.by=index(prices)))
  
}

td <- TREND(aapl$PRC, 5)
summary(td)
```

# Identifying Mean Reversion 

## Indicator ideas 
1. Bollinger Bands 